% v2-acmsmall-sample.tex, dated March 6 2012
% This is a sample file for ACM small trim journals
%
% Compilation using 'acmsmall.cls' - version 1.3 (March 2012), Aptara Inc.
% (c) 2010 Association for Computing Machinery (ACM)
%
% Questions/Suggestions/Feedback should be addressed to => "acmtexsupport@aptaracorp.com".
% Users can also go through the FAQs available on the journal's submission webpage.
%
% Steps to compile: latex, bibtex, latex latex
%
% For tracking purposes => this is v1.3 - March 2012

\documentclass[prodmode,acmtecs]{acmsmall} % Aptara syntax

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}


\usepackage{adjustbox}
\usepackage{array}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{rotating}



\newcommand*\rot{\rotatebox{90}}
\newcommand*\OK[0]{$\surd$}
\newcommand*\NO[0]{$\times$}
\newcommand*\QQ[0]{$?$}

% Metadata Information
\acmVolume{0}
\acmNumber{0}
\acmArticle{0}
\acmYear{2018}
\acmMonth{0}

% Copyright
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{0000001.0000001}

%ISSN
\issn{0360-0300}

\newcommand{\TODO}[1]{{\color{red}{\textbf{TODO: {#1}}\xspace}}}
\newcommand{\QUE}[1]{{\color{blue}{\textbf{Q: {#1}}\xspace}}}


% Document starts
\begin{document}

% Page heads
\markboth{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr}{Modern Graph Generators: A Survey}

% Title portion
%\title{Graph Data Generators in the World of Big Data}
\title{Modern Graph Generators: A Survey}
\author{
ANGELA BONIFATI
\affil{Lyon 1 University, France}
IRENA HOLUBOV\'{A}
\affil{Charles University, Prague, Czech Republic}
ARNAU PRAT-P\'{E}REZ
\affil{DAMA-UPC, Universitat Polit\`ecnica de Catalunya, Spain}
SHERIF SAKR
\affil{University of Tartu, Estonia}
}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

\begin{abstract}
The abundance of interconnected data has fueled the design and
implementation of graph generators reproducing real-world linking
properties, or gauging the effectiveness of graph algorithms, techniques
and applications manipulating these data. We consider graph generation
across multiple subfields, such as graph databases, Semantic Web, social networks, graph streaming, alongside community detection  and graph data analytics. Despite the disparate
requirements of modern graph generators throughout these communities, we
analyze them under a common umbrella, reaching out the functionalities, the
practical usage, and their supported operations.
We argue that this classification is serving the need of providing scientists, researchers and practitioners with the right data generator at hand for their work.

This survey provides a comprehensive overview of the state-of-the-art
modern graph generators by focusing on those that are pertinent and
suitable for several data-intensive tasks. Finally, we discuss open
challenges and missing requirements of current graph generators along with their future extensions to new emerging fields.
\end{abstract}


%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}

<ccs2012>


<concept>

<concept_id>10002950.10003624.10003633</concept_id>
 <concept_desc>Mathematics of computing~Graph theory</concept_desc>

<concept_significance>500</concept_significance>
</concept>

<concept>

<concept_id>10003752.10003809.10003635</concept_id>
 <concept_desc>Theory of computation~Graph algorithms analysis</concept_desc>

<concept_significance>500</concept_significance>
</concept>

<concept>

<concept_id>10002951.10002952.10002953.10010146</concept_id>
 <concept_desc>Information systems~Graph-based database models</concept_desc>

<concept_significance>300</concept_significance>
</concept>
</ccs2012>

\end{CCSXML}



 \ccsdesc[500]{Mathematics of computing~Graph theory}
 \ccsdesc[500]{Theory of computation~Graph algorithms analysis}
 \ccsdesc[300]{Information systems~Graph-based database models}

%
% End generated code
%

% We no longer use \terms command
%\terms{Design, Algorithms, Performance}

\keywords{Big Data management, graph data, generators, benchmarks, synthetic data}

\acmformat{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr, 2018.
Modern Graph Generators: A Survey.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

\begin{bottomstuff}
%This work is supported by ...
Author's addresses:
A. Bonifati, Universit\'{e} Claude Bernard Lyon 1, Liris CNRS Campus La
Doua 23-25 Avenue Pierre de Coubertin, 69622 Villerubanne, France;
I. Holubov\'{a}, Department of Software Engineering, Faculty of Mathematics and Physics, Charles University, Malostransk\'{e} n\'{a}m. 25, 118 00 Praha~1, Czech Republic;
A. Prat-P\'erez, DAMA-UPC, Universitat Polit\`ecnica de Catalunya, Jordi Girona 1-3, 08034 Barcelona, Spain;
S. Sakr, University of Tartu, J Liivi 2, Tartu 50409, Estonia.
\end{bottomstuff}

\maketitle

\input{introduction}
%\input{preliminaries}
\input{comparison}
%\input{classification}
\input{generators}
%\input{comparison2}
\input{data_sets}
\input{challenges}
\input{conclusion}


\begin{acks}
The authors would like to thank Dr. Kamesh Madduri for consultations and suggestions on the covered areas.
\end{acks}

% Bibliography
\bibliographystyle{ACM-Reference-Format-Journals}
\bibliography{biblio}

% History dates
\received{October 2018}{October 2018}{October 2018}


\end{document}
